Challenges to transboundary fisheries management in North America under climate change

### 2020-01-15 Ecol_Manuscript_Draft.Rmd
Re- organized files and folders

```{r Ch3_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

```{r Figure_1, eval = T, echo =F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}

@@

```{r Changes_Per_Species_T, eval=F, echo=F}

@@

```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}

@@

```{r Figure_5, eval = T, echo =F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}

@@

```{r Old analysis, eval = T, echo = T}

@@

```{r IPHC_Proportion_EEZ, eval=F, echo = F, message=F, warning=F}

@@

```{r GB_Results_All, eval=F, echo = F}

>>>>

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

```{r Figure_1, eval = T, echo = F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}

@@

```{r Changes_Per_Species_T, eval = F, echo = F}

@@

```{r Figure_4, eval = T, echo = F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}

@@

```{r Figure_5, eval = T, echo = F, fig.cap="Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)"}

@@

```{r Old analysis, eval = F, echo = F}

@@

```{r IPHC_Proportion_EEZ, eval = F, echo = F, message=F, warning=F}

@@

```{r GB_Results_All, eval = F, echo = F}
